beautier: BEAUti for R

### 2018-01-18 article.tex
Collect feedback

Scientists using \verb;beautier; in a published paper should cite this
article. Users can additionally cite the \verb;beautier; package 
directly. Citation information can be obtained by typing:

@@

from within R.

>>>>

Scientists using \verb;beautier; in a published paper can cite this
article, or cite the \verb;beautier; package 
directly. To obtain this citation from within an R script, use:

@@
